Fourmile Calibrations and Output

### 2025-01-30 params.Rmd
plotted top8 sensitive params between grid and statn, plotted remaining parms for supp

library(tidyverse)
library(plotly)

@@

# 10 most sensitive params

statn <- read_csv('./data/sens_analysis/output_rsa_kge_runoff_statn.csv') %>%
  rename(statn_sens = sensitivity)

@@

special <- join %>%
  slice(1:10)

####

# 10 most sensitive params
params <- read_csv('./38HRU_dec2024_updates/params_weighted_dec2024.csv')

params_filter <- params %>%
  filter(param %in% special$parameter)

@@

>>>>

library(tidyverse)
library(plotly)
library(ggpubr)

@@

# Sensitivity analysis

```{r}
statn <- read_csv('./data/sens_analysis/output_rsa_kge_runoff_statn.csv') %>%
  rename(statn_sens = sensitivity)

@@

# in the average top 10 rank:
# soilOutLPS, snow_trs, lagSurfaceRunoff, a_rain, lagInterflow,
# baseTemp, a_snow, t_factor, soilLatVertLPS, r_factor
# all but the last two are in statn and grids top 10,
# so show the first 8 in the plot
# rest of params show in the supp

# Parameters selected from above

```{r}
# params area weighted (only for lagSurfaceRunoff, a_rain, a_snow)
params <- read_csv('./38HRU_dec2024_updates/params_weighted_dec2024.csv') %>%
  filter(param %in% c('lagSurfaceRunoff',
                      'a_rain',
                      'a_snow')) %>% # select params in the top 8 sens that are area weighted
  rename(value = area_weighted_average,
         input_data = source) %>%
  select(param, input_data, value)

# params unburned (above is params that needed to be area weighted bc burn/unburn)
params_unburn <- read_csv('./38HRU_dec2024_updates/params_unburn.csv') %>%
  filter(param %in% c('soilOutLPS',
                      'snow_trs',
                      'lagInterflow',
                      'baseTemp',
                      't_factor')) %>%
  select(param, input_data, value)

# join the two to get the top 8 sensitve params
param_sens <- bind_rows(params, params_unburn) %>% 
  mutate(input_data = if_else(input_data == 'grid',
                              'Gridded',
                              'Station'))

# get distribution for signf. test
ggplot(param_sens, aes(x = value, fill = input_data)) +
  geom_density(alpha = 0.6) +
  facet_wrap(~param, scales = "free") +
  theme_bw(base_size = 20) +
  scale_fill_manual(values = c("#0047AB", "orange")) +
  theme(
    strip.background = element_blank(),
    panel.grid = element_blank(),
    legend.position = "bottom"
  )

# boxplots of top 8
ggplot(param_sens, aes(x=input_data, y=value, fill=input_data)) +
  geom_boxplot(alpha=0.8,
                outlier.colour = "black") +
  facet_wrap(~param, scales = 'free_y') +
  labs(y=element_blank(),
       x=element_blank()) +
  theme_bw(base_size=20) +
  stat_compare_means(aes(group = input_data),
                     method = "wilcox.test", 
                     label = "p.signif",
                     hide.ns = T,
                     paired = F,
                     #label.y = 0,
                     #label.x = 1.4,
                     size = 7) +
  scale_fill_manual(values = c("#0047AB", "orange")) +
    theme(
    legend.position = 'none',
    #legend.justification = c(0, 1.1), 
    legend.text = element_text(size = 16),
    legend.title = element_blank(), 
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    #strip.text = element_blank()
  ) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))

ggsave('./figures/param_sensit_boxplots.png',
       dpi=600)

# show rest of params for supplemental
# first take area weighted params (except lagSurfaceRunoff, a_rain, a_snow since that is already shown in main fig)
otherParamsWeighted <- read_csv('./38HRU_dec2024_updates/params_weighted_dec2024.csv') %>%
  filter(!param %in% c('lagSurfaceRunoff',
                       'a_rain',
                       'a_snow')) %>%
  rename(value = area_weighted_average,
         input_data = source) %>%
  select(param, input_data, value)

# params that were not affected by burn
otherParams <- read_csv('./38HRU_dec2024_updates/params_unburn.csv') %>%
  filter(!param %in% c('soilOutLPS',
                       'snow_trs',
                       'lagInterflow',
                       'baseTemp',
                       't_factor',
                       'lagSurfaceRunoff',
                       'a_rain',
                       'a_snow')) %>% # these are the ones already shown
  filter(!param %in% otherParamsWeighted$param) %>% # there are the ones that need to be area weighted
  select(param, input_data, value)

# now join the area weighted other to the other params
otherParams <- bind_rows(otherParams, otherParamsWeighted)

# plot the remaning params for catchment
ggplot(otherParams, aes(x=input_data, y=value, fill=input_data)) +
  geom_boxplot(alpha=0.8,
                outlier.colour = "black") +
  facet_wrap(~param, scales = 'free_y',
             ncol=3) +
  labs(y=element_blank(),
       x=element_blank()) +
  theme_bw(base_size=20) +
  stat_compare_means(aes(group = input_data),
                     method = "wilcox.test", 
                     label = "p.signif",
                     hide.ns = T,
                     paired = F,
                     #label.y = 0,
                     #label.x = 1.4,
                     size = 7) +
  scale_fill_manual(values = c("#0047AB", "orange")) +
    theme(
    legend.position = 'none',
    #legend.justification = c(0, 1.1), 
    legend.text = element_text(size = 16),
    legend.title = element_blank(), 
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    #strip.text = element_blank()
  ) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))

ggsave('./figures/remainingparams_boxplots.png',
       dpi=600,
       height=16,
       width=10)

@@

ggsave('./figures/burn_unburn_params.png',
       dpi=600)
